### 2014-06-26 2/literature_review.tex
auto

The propagation of Electro-Magnetic (EM) wave in space is governed by Maxell‚Äôs equations. 
The general solution to these equations is a linear superposition of waves, each having the form of:
\begin{eqnarray*}
 \vec{E}(\vec{r},t) &=& g(\phi(\vec{r},t)) = g(\omega t - \vec{k} \cdot \vec{r}) \\
 \vec{B}(\vec{r},t) &=& g(\phi(\vec{r},t)) = g(\omega t - \vec{k} \cdot \vec{r})
\end{eqnarray*}
where
	$g$ is any well-behaved function of a dimensionless argument $\phi$,
	%for virtually any¬†well-behaved function g¬†of dimensionless argument œÜ, where
	$\omega$ is the angular frequency (in radians per second), and
	$\vec{k}= (k_x,k_y,k_z)$ is the wave vector (in radians per meter).

@@

\begin{equation*}
\vec{E}(z,t) 
= 
\left(
	\begin{array} {c}
		E_x^0 \cos{ \left( wt - kz  + \phi_x^0 \right) } \\
		E_y^0 \cos{ \left( wt - kz  + \phi_y^0 \right)} \\
		0
	\end{array}
\right)
= 
\left(
	\begin{array} {c}
		\xi_x(t) \\
		\xi_y(t) \\
		0
	\end{array}
\right)
\end{equation*}
where $\phi_0$ is the initial phase angle, that is dependent on the choice of space-time origin.

In other words, the EM vector can oscillate in more than one orientation, and this denote the polarization property of EM wave.
The exact shape traced out in a fixed projective plane by the tip of the electric vector as the plane propagate is a description of the polarization state.
This shape is characterized by the formula: 
\begin{equation*}
 \frac{\xi_x^2(t)}{|E_x^0|^2} + \frac{\xi_y^2(t)}{|E_y^0|^2} - 2 \frac{\xi_x \xi_y}{E_x^0 E_y^0} \cos (\Delta \phi) = \sin^2(\Delta \phi)
\end{equation*}
where
	$\Delta \phi = \phi_y^0 - \phi_x^0$
The formula characterizes what is termed as the polarization ellipse.

The parameters that describe the polarization ellipse are: 
\begin{equation*}
\tan (\theta ) = \frac{E_y^0}{E_x^0}
\end{equation*}
with
	$0 \leq \theta \leq \pi/2$. 
The orientation angle, which is the angle between the major semi-axis of the ellipse and the x-axis, is given by:
\begin{equation*}
\tan (\Psi) = \tan (2 \theta) \cos(\Delta \phi)
\end{equation*}
with
	$0 \leq \Psi < \pi$. 
The ellipticity, $\epsilon$ is the major-to-minor-axis ratio.
The ellipticity angle which is defined as $\chi = \arctan (1/\epsilon)$ can be calculated as:
\begin{equation*}
\sin (2 \chi) = \sin(2 \theta) \sin( \Delta \phi)
\end{equation*}
with
	$0 \leq \chi \leq \pi/2$, and $0 \leq \epsilon \leq \infty$

@@

Another way to look at polarization is through the coherency matrix, and equivalently the Stokes matrix.
The wave coherency matrix is defined as:
\begin{equation*}
W_c = \left<
\left(
\begin{array}{c}
 \xi_x \\
 \xi_y
\end{array}
\right)
\left(
\begin{array}{c}
 \xi_x \\
 \xi_y
\end{array}
\right)^{\dagger}
\right>
= \left<
\left(
\begin{array}{c c}
 \xi_x \xi_x^* 	& \xi_x \xi_y^* \\
 \xi_y \xi_x^* 	& \xi_y \xi_y^* 
\end{array}
\right)
\right>
= \left<
\left(
\begin{array}{c c}
 |\xi_x|^2 	& |\xi_x| |\xi_y| e^{-i \Delta \phi} \\
 |\xi_x| |\xi_y| e^{i \Delta \phi} 	& |\xi_y|^2
\end{array}
\right)
\right>
\end{equation*}

The Stokes vector is then defined as:
\begin{equation*}
S_t = 
\left(
\begin{array}{c}
 S_0 \\
 S_1 \\
 S_2 \\
 S_3
\end{array}
\right)
=
\left(
\begin{array}{c}
 |\xi_x|^2 + |\xi_y|^2 \\
 |\xi_x|^2 - |\xi_y|^2 \\
 2\Re(\xi_x \xi_y^*) \\
 2\Im(\xi_x \xi_y^*)
\end{array}
\right)
\end{equation*}

In the case of elementary (or fully polarized) waves, the Stokes vector can be written as:
\begin{equation*}
S_t = 
\left(
\begin{array}{c}
 S_0 \\
 S_0 \cos(2\Psi) \cos(2\chi) \\
 S_0 \sin(2\Psi) \cos(2\chi) \\
 S_0 \sin(2\chi)
\end{array}
\right)
\end{equation*}

@@

In fully polarized wave, the following equation holds:
\begin{equation*}
S_0^2 = S_1^2 + S_2^2 + S_3^2
\end{equation*}

In depolarized wave, it becomes an in-equation
\begin{equation*}
S_0^2 > S_1^2 + S_2^2 + S_3^2
\end{equation*}

Then the degree of polarization is defined as
\begin{equation*}
p = \frac{\sqrt{ S_1^2 + S_2^2 + S_3^2 }}{S_0}
\end{equation*}

In such general case, the Stokes Vector is written as:
\begin{align*}
S_t &= 
\left(
\begin{array}{c}
 I \\
 I p \cos(2\Psi) \cos(2\chi) \\
 I p \sin(2\Psi) \cos(2\chi) \\
 I p \sin(2\chi)
\end{array}
\right) \\
 &= I (1 - p)
\left(
\begin{array}{c}
 1 \\
 0 \\
 0 \\
 0
\end{array}
\right) 
+ I p
\left(
\begin{array}{c}
 1\\
 \cos(2\Psi) \cos(2\chi) \\
 \sin(2\Psi) \cos(2\chi) \\
 \sin(2\chi)
\end{array}
\right)
\end{align*}

@@

POLSAR radar measures the back-scattered echo received as the result of transmitting a signal.
The scattering matrix relates the received signal $E^{Rx}$ with the transmitted $E^{Tx}$ signal as:
\begin{equation*}
 E^{Rx} = \frac{e^{ikr}}{r} S E^{Tx}
\end{equation*}
%***IVM: Hai, do you need to explain the k & r terms?

Normally, horizontal and vertical linear polarization are used for transmission, and thus the scattering matrix, i.e. $S$, would normally have the following expanded form:
\begin{equation*}
 \left( 
\begin{array}{c}
 E_h^{Rx} \\
 E_v^{Rx}
\end{array}
 \right) = \frac{e^{ikr}}{r} 
\left( 
\begin{array}{c c}
 S_{HH} & S_{HV} \\
 S_{VH} & S_{VV}
\end{array}
 \right) 
\left( 
\begin{array}{c}
 E_h^{Tx} \\
 E_v^{Tx}
\end{array}
 \right) 
\end{equation*}

@@

Evidently the two matrices are related:
\begin{equation*}
C_h = N C_v N^T
\end{equation*}
where
	$N = \frac{1}{\sqrt{2}}
\left( 
\begin{array}{c c c}
 1 & 0		& 1\\
 1 & 0		& -1\\
 0 & \sqrt{2}	& 0
\end{array}
\right)$

The off-diagonal values in both covariance and coherence matrices are normally complex numbers. 
Equivalent matrices with all real value entries which carry the same information are called the Mueller and the Kennaugh matrix, which are to be used in forward and backward scattering alignment respectively\cite{Guissard_1994_TGRS}. 
They are defined as the matrix that relates the Stokes matrix of sent and received signals.
\begin{equation*}
S_t^{Rx} = K S_t^{Tx}
\end{equation*}

Since the Stokes and Jones matrices are related, the Kennaugh and Sinclair matrices are also related, and this relationship is given by:
\begin{equation*}
K = 1/2 Q^* S \otimes S^* Q^{T*}
\end{equation*}
where
	$\otimes$ denotes the Kronecker product, and
	$Q = 
\left( 
\begin{array}{c c c c}
 1 & 0 & 0 &  1 \\
 1 & 0 & 0 & -1\\
 0 & 1 & 1 &  0\\
 0 & i & i &  0
\end{array}
\right)$

@@

While the dual-polarization mode sensing has been available operationally for quite some time, partial polarimetry has only recently been investigated in the scientific community. 
In comparison, 
	partial polarimetry measures dual-polarized response from incoming pulses of a single polarization channel,
	while full polarimetry measures the same response from two (generally orthogonal) polarisation channels.
Mathematically, the process is modelled as:
\begin{equation*}
 \left( 
\begin{array}{c}
 E_h^{Rx} \\
 E_v^{Rx}
\end{array}
 \right) = \frac{e^{ikr}}{r} 
\left( 
\begin{array}{c}
 S_{H} \\
 S_{V}
\end{array}
 \right) E^{Tx}
\end{equation*}

@@

\begin{equation*}
J = 
\left(	
\begin{array}{c c}
	|s_{HH}|^2 + |s_{HV}|^2               		& 	{s_{HH}s_{VV}^* + |s_{HV}|^2} \\
	+ 2 \Re{(s_{HH}s_{HV}^*)}          		&  {+ s_{HH}s_{HV}^* + s_{HV}s_{VV}^*}\\
        \vspace{0.01 in} & \vspace{0.01 in}\\
	{s_{HH}^*s_{VV} + |s_{HV}|^2}         		& 	{|s_{VV}|^2 + |s_{HV}|^2}\\
	{+ s_{HV}s_{HH}^* + s_{VV}s_{HV}^*} 	& { + 2 \Re{(s_{VV}s_{HV}^*)}}
\end{array}
\right)
\end{equation*}

%*** IVM, I changed the following reference to a \citet
In \cite{Raney_2006_IGARSS}, Raney demonstrated a different perspective by proposing a hybrid architecture.
He argued that the dual polarisation measurements effectively capture the polarisation states of the single back-scattered signal resulting from a single incoming pulse.
Thus the polarisation choice of the receiving antenna is trivial (as long as they are orthogonal).
The important parameter is the choice of the polarisation to be used for the incoming pulse.
His hybrid architecture is again a kind of partial polarimetry in which the incoming pulse is of circular polarisation, instead of the normally encountered linear polarisation.
The partial covariance matrix then becomes:
\begin{equation*}
J = \frac{1}{2} \left(	
\begin{array}{c c}
	|s_{HH}|^2 + |s_{HV}|^2 
& 	s_{HH}s_{HV}^* - s_{HV}s_{VV}^* \\
        + i (s_{HH}s_{HV}^* - s_{HV}s_{VV}^*)
&       - i (|s_{HV}|^2 + s_{HH}s_{VV}^*) \\ 
        \vspace{0.01 in} & \vspace{0.01 in}\\
	s_{HH}s_{HV}^* - s_{HV}s_{VV}^* 
& 	|s_{VV}|^2 + |s_{HV}|^2  \\
        + i (|s_{HV}|^2 + s_{HH}s_{VV}^*)
&       + i (s_{HV}s_{VV}^* - s_{VV}s_{HV}^*)  
\end{array}
\right)
\end{equation*}

The benefits of this hybrid architecture, according to Raney are that it can measure certain physical polarimetric phenomena such as the odd and even bounce phenomena.
The suggestion is evidenced by calculating the response of known odd-bounce trihedral and even-bounce dihedral when the incident wave is right circular polarized.
\begin{equation*}
\Gamma_{tri} = \left(
\begin{array}{c c}
1 & 0 \\
0 & -1
\end{array}
\right)
\end{equation*}
Then the response will be reversed as it can be calculated as:
\begin{equation*}
J_r = \left(
\begin{array}{c c}
1 & 0 \\
0 & -1
\end{array}
\right) \cdot
\left(
\begin{array}{c}
1 \\
-i
\end{array}
\right) = \left(
\begin{array}{c}
1 \\
i
\end{array}
\right) 
\end{equation*}
with
	$ \left( \begin{array}{c} 1 \\ -i \end{array} \right) $ indicating right circular polarization transmitted, and
	$ \left( \begin{array}{c} 1 \\ i \end{array} \right) $ indicating left circular polarization received.

For a dihedral target, whose main axis is at an angle $\theta$ with respect to the horizontal direction, the Sinclair matrix is given as:
\begin{equation*}
\Gamma_{dih} = 
\left(
\begin{array}{c c}
\cos(2\theta) & \sin(2\theta) \\
\sin(2\theta) & \cos(2\theta)
\end{array}
\right)
\end{equation*}
The even bounce phenomena is detectable as its polarimetric response, which is then:
\begin{equation*}
J_r = \left(
\begin{array}{c c}
\cos(2\theta) & \sin(2\theta) \\
\sin(2\theta) & \cos(2\theta)
\end{array}
\right) \cdot
\left(
\begin{array}{c}
1 \\
-i
\end{array}
\right) = \left(
\begin{array}{c}
1 \\
-i
\end{array}
\right) 
\end{equation*}
In \cite{Raney_2007_IGARSS}, Raney shows that hybrid circular modes bring many conveniences to hardware calibration.
Also in a follow up study \cite{Raney_2007_TGRS}, he demonstrated the classification power of hybrid polarimetry.
Furthermore, Lardeux \cite{Lardeux_2007_ESASP} found that for target classification using SVM techniques, compact polarimetry mode shows comparable results to full polarimetric data.
Notably, the hybrid architectural concept has been adopted and brought towards implementation by NASA's upcoming Desdynl satellite \cite{Raney_2009_RadarConf}.

@@

In the literature, POLSAR data is commonly represented by its covariance matrix.
For full polarimetric SAR data (full-pol) the covariance matrix has the form of
\begin{equation*}
C_3 = 
\begin{bmatrix}
S_{hh}^2 & \sqrt{2}S_{hh}S_{hv}^* & S_{hh}S_{vv}^* \\ 
\sqrt{2}S_{hh}^*S_{hv} &2S_{hv}^2  & \sqrt{2}S_{hv}S_{vv}^*\\ 
S_{hh}^*S_{vv} & \sqrt{2}S_{hv}^*S_{vv} & S_{vv}^2
\end{bmatrix}
\end{equation*}
For partial polarimetric SAR data (part-pol), it reduces to either of the two following equations:
\begin{equation*}
  C_{2,h} =
  \begin{bmatrix}
    S_{hh}^2 & S_{hh}S_{hv}^* \\
    S_{hh}^*S_{hv} & S_{hv}^2
  \end{bmatrix};
  C_{2,v} =
  \begin{bmatrix}
    S_{hv}^2 & S_{hv}S_{vv}^* \\
    S_{hv}^*S_{vv} & S_{vv}^2
  \end{bmatrix}
\end{equation*}
Obviously, the statistical behaviour of $C_3$ can be understood by understanding the behaviour of $C_{2h},C_{2v}$ and
\begin{equation*}
  C_{2,c} = 
\begin{bmatrix}
    S_{hh}^2 & S_{hh}S_{vv}^* \\
    S_{hh}^*S_{vv} & S_{vv}^2
\end{bmatrix}
\end{equation*}

While $C_{2v}, C_{2h}$ are physically related to the Stokes parameters of EM waves,
  $C_{2c}$ is %a totally made-up mathematical term from the full-pol covariance matrix.%***IVM changed it to:
  an artificial term derived from the ful-pol covariance matrix.
In fact, in the field of polarimetric SAR, $C_{2v}, C_{2h}$ are called cross-pol and $C_{2c}$ is called the co-pol covariance matrice.
Their main difference lies in investigating the so-called complex correlation coefficient, defined as:
\begin{equation*}
  \rho = \frac{E \left( S_{pq}S_{rs}^* \right) }{\sqrt{E \left( S^2_{pq} \right) E \left( S^2_{rs} \right) }} = |\rho| e^{j \phi}
\end{equation*}
with $\phi=arg(\rho)$ is the phase difference angle.
In $C_{2v}$ and $C_{2h}$ that are commonly used in optical physics, $|\rho_v|,|\rho_h|$ are insignificant,
  and $\phi_v,\phi_h$ are very random, due to little correlation existing between orthogonal polarizations in monochromatic EM waves.
%By analogy, in POLSAR ``natural surfaces'' data, it is common to consider: $|\rho_v|=|\rho_h|=0$
Their equivalent lies in the ``natural surface'' case of POLSAR,
  where  it is common to assume $|\rho_v|=|\rho_h|=0$.
This is, however, not true in the general case of POLSAR (i.e. including over built-up areas).
Specifically for $C_{2c}$, since there is correlation between the two co-pol channels,
  $|\rho_c|$ is almost always significant and $\phi_c$ is also not entirely random.

@@

The commonly used measure of distance for matrices are either the Euclidean or Manhattan distances, defined as:
\begin{align*}
  d(C_x,C_y) &= \sum_{i,j} |\mathbb{R} (C_x - C_y)_{i,j}| + \sum_{i,j} |\mathbb{I} (C_x - C_y)_{i,j}| \\
  d(C_x,C_y) &= \sqrt{\sum_{i,j} |C_x - C_y|_{i,j}^2 }
\end{align*}
where $C_{i,j}$ denotes the (i,j) elements of the POLSAR covariance matrix C,
 $||$ denotes absolute values
and $\mathbb{R},\mathbb{I}$ denote the real and imaginary parts respectively.
However, in the context of POLSAR% covariance matrix
, these dis-similarity measures are not widely used 
  mainly due to the multiplicative nature of the noisy data.

In the field of POLSAR, the Wishart distance is probably the most widely used, as part of the well-known Wishart classifier \cite{Lee_1999_TGRS}.
It is defined \cite{Lee_1994_IJRS_2299} as:
\begin{equation*}
  d(C_x,C_y) = \ln|C_y| + tr(C_xC_y^{-1})
\end{equation*}
where $tr(C)$ denotes the trace of the matrix C. 
As a measure of distance, its main disadvantage is that $d(C_y,C_y) = \ln|C_y| \neq 0$.

>>>>

The propagation of Electro-Magnetic (EM) wave in space is governed by Maxell‚Äôs equations. 
The general solution to these equations is a linear superposition of waves, each having the form of:
\begin{eqnarray}
 \vec{E}(\vec{r},t) &=& g(\phi(\vec{r},t)) = g(\omega t - \vec{k} \cdot \vec{r}) \\
 \vec{B}(\vec{r},t) &=& g(\phi(\vec{r},t)) = g(\omega t - \vec{k} \cdot \vec{r})
\end{eqnarray}
where
	$g$ is any well-behaved function of a dimensionless argument $\phi$,
	%for virtually any¬†well-behaved function g¬†of dimensionless argument œÜ, where
	$\omega$ is the angular frequency (in radians per second), and
	$\vec{k}= (k_x,k_y,k_z)$ is the wave vector (in radians per meter).

@@

\begin{equation}
\vec{E}(z,t) 
= 
\left(
	\begin{array} {c}
		E_x^0 \cos{ \left( wt - kz  + \phi_x^0 \right) } \\
		E_y^0 \cos{ \left( wt - kz  + \phi_y^0 \right)} \\
		0
	\end{array}
\right)
= 
\left(
	\begin{array} {c}
		\xi_x(t) \\
		\xi_y(t) \\
		0
	\end{array}
\right)
\end{equation}
where $\phi_0$ is the initial phase angle, that is dependent on the choice of space-time origin.

In other words, the EM vector can oscillate in more than one orientation, and this denote the polarization property of EM wave.
The exact shape traced out in a fixed projective plane by the tip of the electric vector as the plane propagate is a description of the polarization state.
This shape is characterized by the formula: 
\begin{equation}
 \frac{\xi_x^2(t)}{|E_x^0|^2} + \frac{\xi_y^2(t)}{|E_y^0|^2} - 2 \frac{\xi_x \xi_y}{E_x^0 E_y^0} \cos (\Delta \phi) = \sin^2(\Delta \phi)
\end{equation}
where
	$\Delta \phi = \phi_y^0 - \phi_x^0$
The formula characterizes what is termed as the polarization ellipse.

The parameters that describe the polarization ellipse are: 
\begin{equation}
\tan (\theta ) = \frac{E_y^0}{E_x^0}
\end{equation}
with
	$0 \leq \theta \leq \pi/2$. 
The orientation angle, which is the angle between the major semi-axis of the ellipse and the x-axis, is given by:
\begin{equation}
\tan (\Psi) = \tan (2 \theta) \cos(\Delta \phi)
\end{equation}
with
	$0 \leq \Psi < \pi$. 
The ellipticity, $\epsilon$ is the major-to-minor-axis ratio.
The ellipticity angle which is defined as $\chi = \arctan (1/\epsilon)$ can be calculated as:
\begin{equation}
\sin (2 \chi) = \sin(2 \theta) \sin( \Delta \phi)
\end{equation}
with
	$0 \leq \chi \leq \pi/2$, and $0 \leq \epsilon \leq \infty$

@@

Another way to look at polarization is through the coherency matrix, and equivalently the Stokes matrix.
The wave coherency matrix is defined as:
\begin{equation}
W_c = \left<
\left(
\begin{array}{c}
 \xi_x \\
 \xi_y
\end{array}
\right)
\left(
\begin{array}{c}
 \xi_x \\
 \xi_y
\end{array}
\right)^{\dagger}
\right>
= \left<
\left(
\begin{array}{c c}
 \xi_x \xi_x^* 	& \xi_x \xi_y^* \\
 \xi_y \xi_x^* 	& \xi_y \xi_y^* 
\end{array}
\right)
\right>
= \left<
\left(
\begin{array}{c c}
 |\xi_x|^2 	& |\xi_x| |\xi_y| e^{-i \Delta \phi} \\
 |\xi_x| |\xi_y| e^{i \Delta \phi} 	& |\xi_y|^2
\end{array}
\right)
\right>
\end{equation}

The Stokes vector is then defined as:
\begin{equation}
S_t = 
\left(
\begin{array}{c}
 S_0 \\
 S_1 \\
 S_2 \\
 S_3
\end{array}
\right)
=
\left(
\begin{array}{c}
 |\xi_x|^2 + |\xi_y|^2 \\
 |\xi_x|^2 - |\xi_y|^2 \\
 2\Re(\xi_x \xi_y^*) \\
 2\Im(\xi_x \xi_y^*)
\end{array}
\right)
\end{equation}

In the case of elementary (or fully polarized) waves, the Stokes vector can be written as:
\begin{equation}
S_t = 
\left(
\begin{array}{c}
 S_0 \\
 S_0 \cos(2\Psi) \cos(2\chi) \\
 S_0 \sin(2\Psi) \cos(2\chi) \\
 S_0 \sin(2\chi)
\end{array}
\right)
\end{equation}

@@

In fully polarized wave, the following equation holds:
\begin{equation}
S_0^2 = S_1^2 + S_2^2 + S_3^2
\end{equation}

In depolarized wave, it becomes an in-equation
\begin{equation}
S_0^2 > S_1^2 + S_2^2 + S_3^2
\end{equation}

Then the degree of polarization is defined as
\begin{equation}
p = \frac{\sqrt{ S_1^2 + S_2^2 + S_3^2 }}{S_0}
\end{equation}

In such general case, the Stokes Vector is written as:
\begin{align}
S_t &= 
\left(
\begin{array}{c}
 I \\
 I p \cos(2\Psi) \cos(2\chi) \\
 I p \sin(2\Psi) \cos(2\chi) \\
 I p \sin(2\chi)
\end{array}
\right) \notag \\
 &= I (1 - p)
\left(
\begin{array}{c}
 1 \\
 0 \\
 0 \\
 0
\end{array}
\right) 
+ I p
\left(
\begin{array}{c}
 1\\
 \cos(2\Psi) \cos(2\chi) \\
 \sin(2\Psi) \cos(2\chi) \\
 \sin(2\chi)
\end{array}
\right)
\end{align}

@@

POLSAR radar measures the back-scattered echo received as the result of transmitting a signal.
The scattering matrix relates the received signal $E^{Rx}$ with the transmitted $E^{Tx}$ signal as:
\begin{equation}
 E^{Rx} = \frac{e^{ikr}}{r} S E^{Tx}
\end{equation}
%***IVM: Hai, do you need to explain the k & r terms?

Normally, horizontal and vertical linear polarization are used for transmission, and thus the scattering matrix, i.e. $S$, would normally have the following expanded form:
\begin{equation}
 \left( 
\begin{array}{c}
 E_h^{Rx} \\
 E_v^{Rx}
\end{array}
 \right) = \frac{e^{ikr}}{r} 
\left( 
\begin{array}{c c}
 S_{HH} & S_{HV} \\
 S_{VH} & S_{VV}
\end{array}
 \right) 
\left( 
\begin{array}{c}
 E_h^{Tx} \\
 E_v^{Tx}
\end{array}
 \right) 
\end{equation}

@@

Evidently the two matrices are related:
\begin{equation}
C_h = N C_v N^T
\end{equation}
where
	$N = \frac{1}{\sqrt{2}}
\left( 
\begin{array}{c c c}
 1 & 0		& 1\\
 1 & 0		& -1\\
 0 & \sqrt{2}	& 0
\end{array}
\right)$

The off-diagonal values in both covariance and coherence matrices are normally complex numbers. 
Equivalent matrices with all real value entries which carry the same information are called the Mueller and the Kennaugh matrix, which are to be used in forward and backward scattering alignment respectively\cite{Guissard_1994_TGRS}. 
They are defined as the matrix that relates the Stokes matrix of sent and received signals.
\begin{equation}
S_t^{Rx} = K S_t^{Tx}
\end{equation}

Since the Stokes and Jones matrices are related, the Kennaugh and Sinclair matrices are also related, and this relationship is given by:
\begin{equation}
K = 1/2 Q^* S \otimes S^* Q^{T*}
\end{equation}
where
	$\otimes$ denotes the Kronecker product, and
	$Q = 
\left( 
\begin{array}{c c c c}
 1 & 0 & 0 &  1 \\
 1 & 0 & 0 & -1\\
 0 & 1 & 1 &  0\\
 0 & i & i &  0
\end{array}
\right)$

@@

While the dual-polarization mode sensing has been available operationally for quite some time, partial polarimetry has only recently been investigated in the scientific community. 
In comparison, 
	partial polarimetry measures dual-polarized response from incoming pulses of a single polarization channel,
	while full polarimetry measures the same response from two (generally orthogonal) polarisation channels.
Mathematically, the process is modelled as:
\begin{equation}
 \left( 
\begin{array}{c}
 E_h^{Rx} \\
 E_v^{Rx}
\end{array}
 \right) = \frac{e^{ikr}}{r} 
\left( 
\begin{array}{c}
 S_{H} \\
 S_{V}
\end{array}
 \right) E^{Tx}
\end{equation}

@@

\begin{equation}
J = 
\left(	
\begin{array}{c c}
	|s_{HH}|^2 + |s_{HV}|^2               		& 	{s_{HH}s_{VV}^* + |s_{HV}|^2} \\
	+ 2 \Re{(s_{HH}s_{HV}^*)}          		&  {+ s_{HH}s_{HV}^* + s_{HV}s_{VV}^*}\\
        \vspace{0.01 in} & \vspace{0.01 in}\\
	{s_{HH}^*s_{VV} + |s_{HV}|^2}         		& 	{|s_{VV}|^2 + |s_{HV}|^2}\\
	{+ s_{HV}s_{HH}^* + s_{VV}s_{HV}^*} 	& { + 2 \Re{(s_{VV}s_{HV}^*)}}
\end{array}
\right)
\end{equation}

%*** IVM, I changed the following reference to a \citet
In \cite{Raney_2006_IGARSS}, Raney demonstrated a different perspective by proposing a hybrid architecture.
He argued that the dual polarisation measurements effectively capture the polarisation states of the single back-scattered signal resulting from a single incoming pulse.
Thus the polarisation choice of the receiving antenna is trivial (as long as they are orthogonal).
The important parameter is the choice of the polarisation to be used for the incoming pulse.
His hybrid architecture is again a kind of partial polarimetry in which the incoming pulse is of circular polarisation, instead of the normally encountered linear polarisation.
The partial covariance matrix then becomes:
\begin{equation}
J = \frac{1}{2} \left(	
\begin{array}{c c}
	|s_{HH}|^2 + |s_{HV}|^2 
& 	s_{HH}s_{HV}^* - s_{HV}s_{VV}^* \\
        + i (s_{HH}s_{HV}^* - s_{HV}s_{VV}^*)
&       - i (|s_{HV}|^2 + s_{HH}s_{VV}^*) \\ 
        \vspace{0.01 in} & \vspace{0.01 in}\\
	s_{HH}s_{HV}^* - s_{HV}s_{VV}^* 
& 	|s_{VV}|^2 + |s_{HV}|^2  \\
        + i (|s_{HV}|^2 + s_{HH}s_{VV}^*)
&       + i (s_{HV}s_{VV}^* - s_{VV}s_{HV}^*)  
\end{array}
\right)
\end{equation}

The benefits of this hybrid architecture, according to Raney are that it can measure certain physical polarimetric phenomena such as the odd and even bounce phenomena.
The suggestion is evidenced by calculating the response of known odd-bounce trihedral and even-bounce dihedral when the incident wave is right circular polarized.
\begin{equation}
\Gamma_{tri} = \left(
\begin{array}{c c}
1 & 0 \\
0 & -1
\end{array}
\right)
\end{equation}
Then the response will be reversed as it can be calculated as:
\begin{equation}
J_r = \left(
\begin{array}{c c}
1 & 0 \\
0 & -1
\end{array}
\right) \cdot
\left(
\begin{array}{c}
1 \\
-i
\end{array}
\right) = \left(
\begin{array}{c}
1 \\
i
\end{array}
\right) 
\end{equation}
with
	$ \left( \begin{array}{c} 1 \\ -i \end{array} \right) $ indicating right circular polarization transmitted, and
	$ \left( \begin{array}{c} 1 \\ i \end{array} \right) $ indicating left circular polarization received.

For a dihedral target, whose main axis is at an angle $\theta$ with respect to the horizontal direction, the Sinclair matrix is given as:
\begin{equation}
\Gamma_{dih} = 
\left(
\begin{array}{c c}
\cos(2\theta) & \sin(2\theta) \\
\sin(2\theta) & \cos(2\theta)
\end{array}
\right)
\end{equation}
The even bounce phenomena is detectable as its polarimetric response, which is then:
\begin{equation}
J_r = \left(
\begin{array}{c c}
\cos(2\theta) & \sin(2\theta) \\
\sin(2\theta) & \cos(2\theta)
\end{array}
\right) \cdot
\left(
\begin{array}{c}
1 \\
-i
\end{array}
\right) = \left(
\begin{array}{c}
1 \\
-i
\end{array}
\right) 
\end{equation}
In \cite{Raney_2007_IGARSS}, Raney shows that hybrid circular modes bring many conveniences to hardware calibration.
Also in a follow up study \cite{Raney_2007_TGRS}, he demonstrated the classification power of hybrid polarimetry.
Furthermore, Lardeux \cite{Lardeux_2007_ESASP} found that for target classification using SVM techniques, compact polarimetry mode shows comparable results to full polarimetric data.
Notably, the hybrid architectural concept has been adopted and brought towards implementation by NASA's upcoming Desdynl satellite \cite{Raney_2009_RadarConf}.

@@

In the literature, POLSAR data is commonly represented by its covariance matrix.
For full polarimetric SAR data (full-pol) the covariance matrix has the form of
\begin{equation}
C_3 = 
\begin{bmatrix}
S_{hh}^2 & \sqrt{2}S_{hh}S_{hv}^* & S_{hh}S_{vv}^* \\ 
\sqrt{2}S_{hh}^*S_{hv} &2S_{hv}^2  & \sqrt{2}S_{hv}S_{vv}^*\\ 
S_{hh}^*S_{vv} & \sqrt{2}S_{hv}^*S_{vv} & S_{vv}^2
\end{bmatrix}
\end{equation}
For partial polarimetric SAR data (part-pol), it reduces to either of the two following equations:
\begin{equation}
  C_{2,h} =
  \begin{bmatrix}
    S_{hh}^2 & S_{hh}S_{hv}^* \\
    S_{hh}^*S_{hv} & S_{hv}^2
  \end{bmatrix};
  C_{2,v} =
  \begin{bmatrix}
    S_{hv}^2 & S_{hv}S_{vv}^* \\
    S_{hv}^*S_{vv} & S_{vv}^2
  \end{bmatrix}
\end{equation}
Obviously, the statistical behaviour of $C_3$ can be understood by understanding the behaviour of $C_{2h},C_{2v}$ and
\begin{equation}
  C_{2,c} = 
\begin{bmatrix}
    S_{hh}^2 & S_{hh}S_{vv}^* \\
    S_{hh}^*S_{vv} & S_{vv}^2
\end{bmatrix}
\end{equation}

While $C_{2v}, C_{2h}$ are physically related to the Stokes parameters of EM waves,
  $C_{2c}$ is %a totally made-up mathematical term from the full-pol covariance matrix.%***IVM changed it to:
  an artificial term derived from the ful-pol covariance matrix.
In fact, in the field of polarimetric SAR, $C_{2v}, C_{2h}$ are called cross-pol and $C_{2c}$ is called the co-pol covariance matrice.
Their main difference lies in investigating the so-called complex correlation coefficient, defined as:
\begin{equation}
  \rho = \frac{E \left( S_{pq}S_{rs}^* \right) }{\sqrt{E \left( S^2_{pq} \right) E \left( S^2_{rs} \right) }} = |\rho| e^{j \phi}
\end{equation}
with $\phi=arg(\rho)$ is the phase difference angle.
In $C_{2v}$ and $C_{2h}$ that are commonly used in optical physics, $|\rho_v|,|\rho_h|$ are insignificant,
  and $\phi_v,\phi_h$ are very random, due to little correlation existing between orthogonal polarizations in monochromatic EM waves.
%By analogy, in POLSAR ``natural surfaces'' data, it is common to consider: $|\rho_v|=|\rho_h|=0$
Their equivalent lies in the ``natural surface'' case of POLSAR,
  where  it is common to assume $|\rho_v|=|\rho_h|=0$.
This is, however, not true in the general case of POLSAR (i.e. including over built-up areas).
Specifically for $C_{2c}$, since there is correlation between the two co-pol channels,
  $|\rho_c|$ is almost always significant and $\phi_c$ is also not entirely random.

@@

The commonly used measure of distance for matrices are either the Euclidean or Manhattan distances, defined as:
\begin{align}
  d(C_x,C_y) &= \sum_{i,j} |\mathbb{R} (C_x - C_y)_{i,j}| + \sum_{i,j} |\mathbb{I} (C_x - C_y)_{i,j}| \\
  d(C_x,C_y) &= \sqrt{\sum_{i,j} |C_x - C_y|_{i,j}^2 }
\end{align}
where $C_{i,j}$ denotes the (i,j) elements of the POLSAR covariance matrix C,
 $||$ denotes absolute values
and $\mathbb{R},\mathbb{I}$ denote the real and imaginary parts respectively.
However, in the context of POLSAR% covariance matrix
, these dis-similarity measures are not widely used 
  mainly due to the multiplicative nature of the noisy data.

In the field of POLSAR, the Wishart distance is probably the most widely used, as part of the well-known Wishart classifier \cite{Lee_1999_TGRS}.
It is defined \cite{Lee_1994_IJRS_2299} as:
\begin{equation}
  d(C_x,C_y) = \ln|C_y| + tr(C_xC_y^{-1})
\end{equation}
where $tr(C)$ denotes the trace of the matrix C. 
As a measure of distance, its main disadvantage is that $d(C_y,C_y) = \ln|C_y| \neq 0$.
